---
title: "HCP tasks trait complete results"
output: pdf_document
fontsize: 10pt
date: "`r Sys.Date()`"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options("width"=95)
options(scipen = 999, digits = 7) 
```



```{r load packages and data, echo= FALSE, include=FALSE}

#setwd("/")
library(tidyverse)
library(tidyr)
library(knitr)
library(dplyr)
library(tinytex)

library(ggplot2)
library(ggrepel)
library(gridExtra)
library(MetBrewer)
library(viridis)

library(lmerTest)
library(emmeans)
library(MASS)

df<-read.csv("/hcp_task_trait/data/hcp_analysis_df_spearman.csv", sep = ",")

df$sub<-as.factor(c(df$sub))
df$cont<-gsub("tom", "ToM", df$cont)
df$cont<-gsub("rel", "relational", df$cont)
df$cont<-gsub("avg", "motor", df$cont)
df$cont<-gsub("0bk", "0back", df$cont)
df$cont<-gsub("2bk", "2back", df$cont)
cont_list<- levels(as.factor(df$cont))

df$Gender<-as.factor(c(df$Gender))
df$cont<-as.factor(c(df$cont))
df$Mother_ID<-as.factor(c(df$Mother_ID))
df$Father_ID<-as.factor(c(df$Father_ID))
df$Family_ID<-as.factor(c(df$Family_ID))
df$Zygosity<-as.factor(c(df$Zygosity))


df$corr_g1<-as.numeric(df$corr_g1)
df$corr_g2<-as.numeric(df$corr_g2)
df$corr_g3<-as.numeric(df$corr_g3)
df$motion<-as.numeric(df$motion)

```

```{r create sumdf to keep means, sd se etc handy, echo=FALSE}
my_sum1 <- df %>%
  group_by(cont) %>%
  summarise( 
    n=n(),
    mean=mean(as.numeric(corr_g1)),
    sd=sd(as.numeric(corr_g1))
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1)) 


my_sum2 <- df %>%
  group_by(cont) %>%
  summarise( 
    n=n(),
    mean=mean(as.numeric(corr_g2)),
    sd=sd(as.numeric(corr_g2))
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1)) 

my_sum3 <- df %>%
  group_by(cont) %>%
  summarise( 
    n=n(),
    mean=mean(as.numeric(corr_g3)),
    sd=sd(as.numeric(corr_g3))
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1)) 

sumdf<-data.frame(cont=my_sum1$cont,
                   g1_mean=my_sum1$mean, g2_mean=my_sum2$mean, g3_mean=my_sum3$mean,
                   g1_sd=my_sum1$sd, g2_sd=my_sum2$sd, g3_sd=my_sum3$sd,
                   g1_se=my_sum1$se, g2_se=my_sum2$se, g3_se=my_sum3$se)
```


## Main dimension-specific ANOVAs
```{r, echo=T}


mod1<-lmerTest::lmer(corr_g1~ (1|sub)+ (1|Family_ID)+ cont + Age + Gender + motion +  
                         Neuroticism + Openness + Conscientiousness +Extraversion + Agreeableness +
                         cont:Neuroticism+ cont:Openness+ cont:Conscientiousness + cont:Extraversion+   
                         cont:Agreeableness, data = df)




mod2<-lmerTest::lmer(corr_g2~ (1|sub)+ (1|Family_ID)+ cont + Age + Gender + motion +  
                         Neuroticism + Openness + Conscientiousness +Extraversion + Agreeableness +
                         cont:Neuroticism+ cont:Openness+ cont:Conscientiousness + cont:Extraversion+   
                         cont:Agreeableness, data = df)



mod3<-lmerTest::lmer(corr_g3~ (1|sub)+ (1|Family_ID)+ cont + Age + Gender + motion +  
                         Neuroticism + Openness + Conscientiousness +Extraversion + Agreeableness +
                         cont:Neuroticism+ cont:Openness+ cont:Conscientiousness + cont:Extraversion+   
                         cont:Agreeableness, data = df)

```

### D1 
```{r, echo=F}
anova1<-anova(mod1)
p1<-kable(anova(mod1), "simple",  align= "lrrrrrr", digits = 7 )
p1

```

### D2 
```{r, echo=F}
anova2<-anova(mod2)
p2<-kable(anova(mod2), "simple",  align= "lrrrrrr", digits = 7 )
p2
```

### D3
```{r, echo=F}
anova3<-anova(mod3)
p3<-kable(anova(mod3), "simple",  align= "lrrrrrr", digits = 7 )
p3

```

\newpage
## contrast-specific trait slopes
### D1 contrast locations, and contrast-specific slopes
```{r, echo=T}

emm_options(lmerTest.limit = 13081, lmer.df = "satterthwaite")
em1cont<-emmeans(mod1, ~ cont, type = "response")
em1contpairs<-pairs(em1cont, infer = TRUE)

em1NEO_N<-emtrends(mod1, "cont",  var="Neuroticism", adjust="none", infer = TRUE)
em1NEO_O<-emtrends(mod1, "cont",  var="Openness", adjust = "none", infer = TRUE)
em1NEO_C<-emtrends(mod1, "cont",  var="Conscientiousness", adjust = "none", infer = TRUE)
em1NEO_E<-emtrends(mod1, "cont",  var="Extraversion", adjust = "none", infer = TRUE)
em1NEO_A<-emtrends(mod1, "cont",  var="Agreeableness", adjust = "none", infer = TRUE)
```

```{r, echo=F}

kable(em1cont, "simple",  align= "lrrrrr", digits = 4 )

kable(em1NEO_N, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em1NEO_O, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em1NEO_C, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em1NEO_E, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em1NEO_A, "simple",  align= "lrrrrrrr", digits = 7 )

```

\newpage
### D2 contrast locations, and contrast-specific slopes
```{r, echo= T}

emm_options(lmerTest.limit = 13201, lmer.df = "satterthwaite")
em2cont<-emmeans(mod2, ~ cont, type = "response")
em2contpairs<-pairs(em2cont, adjust = "bonferroni", infer = TRUE)

em2NEO_N<-emtrends(mod2, "cont",  var="Neuroticism", adjust="none", infer = TRUE)
em2NEO_O<-emtrends(mod2, "cont", var="Openness", adjust = "none", infer = TRUE)
em2NEO_C<-emtrends(mod2, "cont",  var="Conscientiousness", adjust = "none", infer = TRUE)
em2NEO_E<-emtrends(mod2, "cont",  var="Extraversion", adjust = "none", infer = TRUE)
em2NEO_A<-emtrends(mod2, "cont",  var="Agreeableness", adjust = "none", infer = TRUE)
```

```{r, echo=F}
kable(em2cont, "simple",  align= "lrrrrr", digits = 4 )

kable(em2NEO_N, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em2NEO_O, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em2NEO_C, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em2NEO_E, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em2NEO_A, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D3 contrast locations, and contrast-specific slopes
```{r, echo= T}
emm_options(lmerTest.limit = 13201, lmer.df = "satterthwaite")
em3cont<-emmeans(mod3, ~ cont, type = "response")
em3contpairs<-pairs(em3cont, adjust = "bonferroni", infer = TRUE)

em3NEO_N<-emtrends(mod3, "cont",  var="Neuroticism", adjust="none", infer = TRUE)
em3NEO_O<-emtrends(mod3, "cont",  var="Openness", adjust = "none", infer = TRUE)
em3NEO_C<-emtrends(mod3, "cont",  var="Conscientiousness", adjust = "none", infer = TRUE)
em3NEO_E<-emtrends(mod3, "cont",  var="Extraversion", adjust = "none", infer = TRUE)
em3NEO_A<-emtrends(mod3, "cont",  var="Agreeableness", adjust = "none", infer = TRUE)
```

```{r, echo=F}
kable(em3cont, "simple",  align= "lrrrrr", digits = 4 )

kable(em3NEO_N, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em3NEO_O, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em3NEO_C, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em3NEO_E, "simple",  align= "lrrrrrrr", digits = 7 )
kable(em3NEO_A, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
## pairwise interaction effects
### D1
```{r, echo=T}
em1int_NEO_N<-emtrends(mod1, pairwise~cont,  var="Neuroticism", adjust="none", infer = TRUE)
em1int_NEO_O<-emtrends(mod1, pairwise~cont, var="Openness", adjust = "none", infer = TRUE)
em1int_NEO_C<-emtrends(mod1, pairwise~cont,  var="Conscientiousness", adjust="none", infer = TRUE)
em1int_NEO_E<-emtrends(mod1, pairwise~cont, var="Extraversion", adjust = "none", infer = TRUE) 
em1int_NEO_A<-emtrends(mod1, pairwise~cont,  var="Agreeableness", adjust="none", infer = TRUE)
```

\newpage
### D1 contrast- pairwise trait effects : Neuroticism 
```{r, echo=T}
kable(em1int_NEO_N$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D1 contrast- pairwise trait effects : Openness
```{r, echo=T}
kable(em1int_NEO_O$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D1 contrast- pairwise trait effects : Conscientiousness 
```{r, echo=T}
kable(em1int_NEO_C$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D1 contrast- pairwise trait effects : Extraversion
```{r, echo=T}
kable(em1int_NEO_E$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D1 contrast- pairwise trait effects :Agreeablness
```{r, echo=T}
kable(em1int_NEO_A$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
## D2
```{r, echo=T}
em2int_NEO_N<-emtrends(mod2, pairwise~cont,  var="Neuroticism", adjust="none", infer = TRUE)
em2int_NEO_O<-emtrends(mod2, pairwise~cont, var="Openness", adjust = "none", infer = TRUE)
em2int_NEO_C<-emtrends(mod2, pairwise~cont,  var="Conscientiousness", adjust="none", infer = TRUE)
em2int_NEO_E<-emtrends(mod2, pairwise~cont, var="Extraversion", adjust = "none", infer = TRUE) 
em2int_NEO_A<-emtrends(mod2, pairwise~cont,  var="Agreeableness", adjust="none", infer = TRUE)

```

\newpage
### D2 contrast- pairwise trait effects : Neuroticism 
```{r, echo=T}
kable(em2int_NEO_N$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D2 contrast- pairwise trait effects : Openness
```{r, echo=T}
kable(em2int_NEO_O$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D2 contrast- pairwise trait effects : Conscientiousness 
```{r, echo=T}
kable(em2int_NEO_C$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D2 contrast- pairwise trait effects : Extraversion
```{r, echo=T}
kable(em2int_NEO_E$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D2 contrast- pairwise trait effects :Agreeablness
```{r, echo=T}
kable(em2int_NEO_A$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
## D3
```{r, echo=T}
em3int_NEO_N<-emtrends(mod3, pairwise~cont,  var="Neuroticism", adjust="none", infer = TRUE)
em3int_NEO_O<-emtrends(mod3, pairwise~cont, var="Openness", adjust = "none", infer = TRUE)
em3int_NEO_C<-emtrends(mod3, pairwise~cont,  var="Conscientiousness", adjust="none", infer = TRUE)
em3int_NEO_E<-emtrends(mod3, pairwise~cont, var="Extraversion", adjust = "none", infer = TRUE) 
em3int_NEO_A<-emtrends(mod3, pairwise~cont,  var="Agreeableness", adjust="none", infer = TRUE)
```

\newpage
### D3 contrast- pairwise trait effects : Neuroticism 
```{r, echo=T}
kable(em3int_NEO_N$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D3 contrast- pairwise trait effects : Openness
```{r, echo=T}
kable(em3int_NEO_O$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D3 contrast- pairwise trait effects : Conscientiousness 
```{r, echo=T}
kable(em3int_NEO_C$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D3 contrast- pairwise trait effects : Extraversion
```{r, echo=T}
kable(em3int_NEO_E$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

\newpage
### D3 contrast- pairwise trait effects :Agreeablness
```{r, echo=T}
kable(em3int_NEO_A$contrasts, "simple",  align= "lrrrrrrr", digits = 7 )
```

